\documentclass{article}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{fullpage}          		% fullpage margins

\usepackage[ampersand]{easylist}

\newcommand{\tab}{\hspace{.2\textwidth}}

\begin{document}
\title{Apartment Checklist}
\author{Hai.D.}
\maketitle

List of things to do:\\
\begin{easylist}[checklist]
	\ListProperties(Hide=100, Hang=true, Progressive=10ex, 
		Style*= {$\square$} ,
		Style2*= $\bullet$,
		Style3*= --)
		
	& Lots of pics of everything from multi angles
    & Check light switches
    & Check cold/hot water pressure of all faucets and shower %(in psi units)
    & Flush Toilet %(check direction of water spin)
    & Check the Stove %(cook breakfast)
    & Look for signs of Pest%(check cabinets? : Make mating calls) 
    & Check outlets with phone charger 
    & Maybe ask why the current tennants are leaving/have left?  
    & Ask about the neighbors.
	& Landlord Information
    && Name
    && Contact \#
	& Other information:
	&& 
	&&
	& When you are viewing the studio, let him know you're doing it for a friend.
    & At the end please ask about the application process and mention that he will have a cosigner 	
	\\\\
\end{easylist}

List of things to ask and check for:\\
\begin{easylist}[checklist]
	\ListProperties(Hide=100, Hang=true, Progressive=10ex, 
		Style*= {$\square$ $\square$}  ,
		Style2*= $\bullet$,
		Style3*= -- )

    & Is it possible to trip a breaker? Short a fuse?

    & Check appliances if any 
    && refrigerator
    && stove/oven
    && microwave
    & Quiet hours
    & Water heater (Is it shared? Where is it? Case scenario it breaks?)
    & Fire escape / Fire detectors / Carbon monoxide detectors
    & Is a bed provided?
    & What can you tell me about the neighbors?
    & Are windows working and well sealed?  
    & The floor -(clean carpet?) 
    & Lock on main door
    & Garbage removal
    & Parking
    & Laundry facilities(clean? How far?) 
    & Comfortable overall? (wear pajama pants)
    & Security Deposit
    & Upfront Deposit?
    & First Month's/Last Month's Rent
    & Renter's Insurance or Additional fees?
    & Late fee
    & Leasing Details
    & Amenities and Accomodations
    && Wifi
    && AC
    && Heating
    & Bills 
    && Water
    && Heating
    && Electricity
    && Internet/Cable
    && Gas
    & Elevator
    & Mailroom   
    \\    
\end{easylist}





%\mbox{\ooalign{$\checkmark$\cr\hidewidth$\square$\hidewidth\cr}}
%\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$}

\end{document}